Discrete Quantum Theories and Computing

### 2018-12-05 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Add more comments...

In conventional quantum theory and computation, the probability amplitudes
are modeled by the continuum of complex numbers. This kind of model
doesn't take into account that human doesn't have the ability to distinguish
quantities differing only by an arbitrarily small extent. One possibility
is that the probability amplitudes in quantum theories are quantized.
This leads us to consider quantum theories and computing over finite
fields. Even if the probability amplitudes are actually continuous,
since human has no ability to distinguish the probability computed
by these probability amplitudes, it may be desirable to incorporate
the idea of measurement precision into the quantum theory, and consider
quantum interval-valued probability.
\begin{sidewaystable}
\caption{Comparison among our models, where the upper half of the table lists
their quantum mechanical definitions and properties, and the lower
half of the table lists their computational power.}

>>>>

In conventional quantum theory and computation, the probability amplitudes\todo{We
haven't said the probability amplitudes in the first paragraph in
our previous papers. I may need to replace it by a term which is not
that technical? } are modeled by the continuum of complex numbers.
This kind of model doesn't take into account that human doesn't have
the ability to distinguish quantities differing only by an arbitrarily
small extent~\cite{Turing_1937,Gisin2017}. One possibility is that
the probability amplitudes in quantum theories are quantized. This
leads us to consider quantum theories and computing over finite fields.
Even if the probability amplitudes are actually continuous, since
human has no ability to distinguish the probability computed by these
probability amplitudes, it may be desirable to incorporate the idea
of measurement precision into the quantum theory, and consider quantum
interval-valued probability.
\begin{sidewaystable}
\caption{Comparison among our models, where the upper half of the table lists
their quantum mechanical definitions and properties, and the lower
half of the table lists their computational power.}
